HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2023-02-01 tmlr_submission/hermes_paper_submission/hermes_paper.tex
Minor modifications Sections 1 and 2

\begin{figure*}
  \centering
    \includegraphics[width=1.\linewidth]{pipeline_archi}
  \caption{From social media to fashion time series. a) A complete image dataset of 150 millions of pictures is collected from social media users localized on 5 strategic markets. b) A visual recognition pipeline is applying on images. Global fashion items are detected with a collection of fine-grain attributes. c) Result are aggregated by fashion trend definition over the time and normalized in order to remove social media bias. The fashion time series are created.}
\label{fig:pipeline}
\end{figure*}

@@

Social media have appeared as an impressive data source to follow the evolution of fashion over the time. Looking at a specific trend, social media can provide where and when this trend had been worn at first and how it spread all over the world. To do it automatically for thousands of trends, the following methodology was introduced. In the first place, a complete image dataset of 150 millions pictures is collected from different social media such as Instagram or Weibo. We targeted 5 strategic markets for the retail industry using posts localisation: the United States, Europe, Japan, Brazil and China. 
The second step consists in creating a powerful visual recognition framework to be able to detect clothes details on pictures like the type of clothing, the form, the size, the color, the texture, etc. To do so, the following framework is designed.
\begin{enumerate}
    \item First, an object detection model is trained to detect the position, the size and the general type of possible multiple fashion items on a picture. This localization model is based on the Faster-RCNN architecture introduced in \citet{ren2015}. Starting from weights trained on MS-COCO \citep{lin2014}, a fine-tune of the model is done on our data with a standard setup following the original paper.
    \item  Additionally, several visual recognition models are trained at classifying a rich collection of 350 fashion details. We train one classifier for each category of fashion item: one for pants, another for tops, a third for shoes, etc. These models are all based on the Xception architecture introduced in \citet{chollet2017}. So as to trained them, large amount of social media pictures (between 200k and 800k training images depending on the category) have been manually tagged to constitute meaningful training datasets depending on the classification task. Architectures are first initialized with public weights trained on ImageNet \citep{russakovsky2014} and then fine tuned on the manually labeled dataset corresponding to their task.
\end{enumerate}

@@

The 150 million of social media pictures are analyzed with the visual recognition pipeline described below. Out of those images, we detected clothes in 96 millions posts making the final dataset used in this paper. We aggregate results by fashion trend definition over the time and  thousands of trends are finally translated from social media to time series. We note $y^{c,g,m,i}$ the final raw sequence representing the fashion trend $i$ of the cloth type $c$ for the gender $g$ on market $m$. At each time t, $y^{c,g,m,i}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $i$ of the cloth type $c$ for the gender $g$. As an illustration, an example of fashion time series is given in Figure~\ref{fig:oneemergingtrend}.

@@

Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences $y^{c,g,m,i}$ in order to remove bias. Thus, we define the following normalizing signal $\Tilde{y}^{c,g,m}$. This signal represents the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe). With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \citep{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$. The resulting deseasonalized signal is called  $\bar{y}^{c,g,m}$. Finally, for any fashion trend $i$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
\begin{equation}
    y^{i}_t = \frac{y^{c,g,m,i}_{t}}{\bar{y}^{c,g,m}_t}\,,
\end{equation}
where T denotes the number of available time steps. The time series $y^{c,g,m,i}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences. With this normalizing step, a majority of the social media bias are removed and the final normalized sequences are expressed in share of category. As an illustration, an example of the normalization process is displayed in Figure~\ref{fig:normalization}. The raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China.

@@

In theoretical fashion dynamics \citep{rogers1962}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
So as too catch the early signal of the emergence of a trend, 6000 social media influencers were selectioned by hand by fashion experts. Aggregating them, a specific ``fashion-oriented`` panel is created. With the same methodology as for the main panel described in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created. We named \textit{fashion-forwards} this weak signal.  For all fashion sequence $\{y^i_t\}_{1 \leq t \leq T}$, let $\{\ts^{f,i}_t\}_{1 \leq t \leq T}$ be the normalized sequence representing the behaviours of influencers regarding the fashion trend $i$. As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for the hybrid model: for all $t \in \{1,\ldots,T\}$ and any fashion trend $i$,
$$
\ws^{f,i}_{t} = \frac{\ts_t^{f,i}}{\ts_t^{f,i}+\ts_t^{i}}\,.
$$
where T denotes the number of available time steps. Values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel. For instance, an impressive emerging fashion shoes trend with its \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.

>>>>

\begin{figure*}
  \centering
    \includegraphics[width=1.\linewidth]{pipeline_archi}
  \caption{From social media to fashion time series. a) A complete image dataset of 150 millions of pictures is collected from social media users localized on 5 strategic markets. b) A visual recognition pipeline is applied on images. Global fashion items are detected with a collection of fine-grain attributes. c) Results are aggregated by fashion trend over time and normalized in order to remove social media bias. }
\label{fig:pipeline}
\end{figure*}

@@

Social media have appeared as an impressive data source to follow the evolution of fashion over the time. Looking at a specific trend, social media can provide where and when this trend had been worn at first and how it spread all over the world. To do it automatically for thousands of trends, the following methodology was introduced. In the first place, a complete image dataset of 150 millions pictures is collected from different social media such as Instagram or Weibo. We targeted 5 strategic markets for the retail industry using posts localisation: the United States, Europe, Japan, Brazil and China. 
The second step consists in creating a powerful visual recognition framework to be able to detect clothes details on pictures like the type of clothing, the form, the size, the color, the texture, etc. To do so, the following framework is designed.
\begin{enumerate}
    \item First, an object detection model is trained to detect the position, the size and the general type of possible multiple fashion items on a picture. This localization model is based on the Faster-RCNN architecture introduced in \citet{ren2015}. Starting from weights trained on MS-COCO \citep{lin2014}, the model is fine-tuned with our data with a standard setup following the original paper.
    \item  Additionally, several visual recognition models are trained at classifying a rich collection of 350 fashion details. We train one classifier for each category of fashion item: one for pants, another for tops, a third for shoes, etc. These models are all based on the Xception architecture introduced in \citet{chollet2017}. So as to trained them, large amount of social media pictures (between 200k and 800k training images depending on the category) have been manually tagged to constitute meaningful training datasets depending on the classification task. Architectures are first initialized with public weights trained on ImageNet \citep{russakovsky2014} and then fine tuned on the manually labeled dataset corresponding to their task.
\end{enumerate}

@@

The 150 million of social media pictures are analyzed with this visual recognition pipeline. Out of those images, we detected clothes in 96 millions posts making the final dataset used in this paper. We aggregate results by fashion trend definition over the time and  thousands of trends are finally translated from social media to time series. We note $y^{c,g,m,i}$ the final raw sequence representing the fashion trend $i$ of the cloth type $c$ for the gender $g$ on market $m$. At each time t, $y^{c,g,m,i}_t$ represents the number of posted pictures in the market $m$ during the week $t$ where computer vision algorithms detected the fashion trend $i$ of the cloth type $c$ for the gender $g$. As an illustration, an example of fashion time series is given in Figure~\ref{fig:oneemergingtrend}.

@@

Due to the increasing use of social media and continuous changes of users' behaviours, a normalization step is applied to the raw sequences $y^{c,g,m,i}$ in order to remove bias. Thus, we define the following normalizing signal $\Tilde{y}^{c,g,m}$. This signal represents the global sequence of the cloth type $c$ for the gender $g$ on market $m$ (e.g the evolution of the skirts in general for female in Europe). With the R package \texttt{stats}, the Seasonal-Trend decomposition using LOESS  \citep{cleveland1990} is used to remove the seasonal component of $\Tilde{y}^{c,g,m}$. The resulting deseasonalized signal is called  $\bar{y}^{c,g,m}$. Finally, for any fashion trend $i$, the following normalized sequence is defined for all $ 0 \leq t \leq T$:
\begin{equation}
    y^{i}_t = \frac{y^{c,g,m,i}_{t}}{\bar{y}^{c,g,m}_t}\,,
\end{equation}
where T denotes the number of available time steps. The time series $y^{c,g,m,i}$ is divided by the deseasonalized signal $\bar{y}^{c,g,m}$ and not $\Tilde{y}^{c,g,m}$ in order to avoid removing the seasonality of all the fashion trend sequences. With this normalizing step, most of the social media bias is removed and the final normalized sequences are expressed in share of category. As an illustration, an example of the normalization process is displayed in Figure~\ref{fig:normalization}. The raw Jersey Top trend for females in China is divided by the deseasonalized global Top trend for females in China.

@@

In theoretical fashion dynamics \citep{rogers1962}, different categories of adopters follow a trend in succession, resulting in several adoption waves.
So as too catch the early signal of the emergence of a trend, 6000 social media influencers were selectioned by hand by fashion experts. Aggregating them, a specific ``fashion-oriented`` panel is created. With the same methodology as for the main panel described in Section~\ref{sec:dataset:a} and Section~\ref{sec:dataset:b}, a normalized time series representing each fashion trend on this specific population is created. We named \textit{fashion-forwards} this weak signal.  For all fashion sequence $\{y^i_t\}_{1 \leq t \leq T}$, let $\{\ts^{f,i}_t\}_{1 \leq t \leq T}$ be the normalized sequence representing the behaviours of influencers regarding the fashion trend $i$. As we want to detect shifts between the main signal and the fashion forward signal, the following input is computed for the hybrid model: for all $t \in \{1,\ldots,T\}$ and any fashion trend $i$,
$$
\ws^{f,i}_{t} = \frac{\ts_t^{f,i}}{\ts_t^{f,i}+\ts_t^{i}}\,.
$$
where T denotes the number of available time steps. Values close to 0.5 indicate a similar behaviour between the influencers panel and the general panel. For instance, an  emerging fashion shoes trend with its \textit{fashion-forwards} weak signal is represented in Figure~\ref{fig:oneemergingtrend}.
